### 2022-11-10 paper-thesis/chapters/20-adding-booleans.tex
Reindex chapters + writing

\begin{lstlisting}
BoolType : Expr
BoolFalse : Expr
BoolTrue : Expr
BoolIf : Expr * Expr * Expr -> Expr
\end{lstlisting}
Then, the rules for beta reducing the language are in figure \ref{fig:bool-rules-beta}. There is one particularly interesting case, that is how to beta-reduce if statements. Converting this rule to Statix is not entirely trivial, since you need to choose which rule to apply based on what \verb|c| evaluates to. A new rule is needed, which has 3 cases. One for if \verb|c| evaluates to true, one for if \verb|c| evaluates to false, and finally a third case for other cases (such as when \verb|c| is a variable that does not have a substitution). Remember that \verb|rebuild| is the rule introduced in chapter \ref{chap:baselang}, which takes a scoped expression and a list of arguments and converts it to an expression by adding \verb|FnDestruct|s. These rules are stated below:

@@

>>>>

\begin{lstlisting}
BoolType : Expr
BoolFalse : Expr
BoolTrue : Expr
BoolIf : Expr * Expr * Expr -> Expr
\end{lstlisting}
Then, the rules for beta reducing the language are in figure \ref{fig:bool-rules-beta}. There is one particularly interesting case, that is how to beta-reduce if statements. Converting this rule to Statix is not entirely trivial, since you need to choose which rule to apply based on what \verb|c| evaluates to. A new rule is needed, which has 3 cases. One for if \verb|c| evaluates to true, one for if \verb|c| evaluates to false, and finally a third case for other cases (such as when \verb|c| is a variable that does not have a substitution). These rules are stated below: (Remember that \verb|rebuild| is the rule introduced in chapter \ref{chap:baselang}, which takes a scoped expression and a list of arguments and converts it to an expression by adding \verb|FnDestruct|s)

@@

Next, the rules for type-checking booleans are in figure \ref{fig:bool-rules-typecheck}, which are relatively simple. The if expression checks that both branches have the same type, as it is a non-dependent if statement.

\begin{figure}[ht]
\begin{mathpar}
	\inferrule{
	} {
		\toe{s}{BoolType()}{Type()}
	}

	\inferrule{
	} {
		\toe{s}{BoolTrue()}{BoolType()}
	}

	\inferrule{
	} {
		\toe{s}{BoolFalse()}{BoolType()}
	}

	\inferrule{
		\toe{s}{c}{ct}
		\\\beq{ct}{BoolType()}
		\\\\
		\\\toe{s}{b1}{tb1}
		\\\toe{s}{b2}{tb2}
		\\\beq{tb1}{tb2}
	} {
		\toe{s}{BoolIf(c, b1, b2)}{tb1}
	}
\end{mathpar}
\caption{Rules for type checking booleans}
\label{fig:bool-rules-typecheck}
\end{figure}

### 2022-11-10 paper-thesis/chapters/21-adding-inference.tex
Reindex chapters + writing

\chapter{Inference}

\section{Background: What is inference?}

Inference

\section{General inference in Statix}
\label{general-inference}

\section{Greedy inference}

Instead, we implement a strategy that I would like to call greedy inference (TODO: does this have a name?).

@@

First, we introduce a new constructor, \verb|Infer : Expr -> Expr|. This will be used to store metavariables which we want to infer. This is a hack we use, ideally we would like to query statix to see if a metavariable is initialized, but as discussed in section \ref{general-inference} this is not possible.

@@

\section{Analysis: How well does it work?}

>>>>

\chapter{Term Inference}

Inference is an important feature of dependent programming languages, that allows redundant parts of programs to be left out. For example, it allows you to infer the arguments of a function, if they can be inferred by the arguments that follow, like here where the type of the argument can be inferred, since we pass it \verb|true| which is a boolean:
\begin{lstlisting}
let id = (\T : Type. \x: T. x);
id _ true
\end{lstlisting}

We call it \emph{term inference} rather than \emph{type inference}, because we can infer values other than types. For example, it can infer that the \verb|_| in this example must be \verb|true|:
\begin{lstlisting}
postulate f: Bool -> Type;
postulate g: f true -> Type;
\x: f _. g x
\end{lstlisting}

\section{Different sorts of inference}
\label{strength-inference}

The strength of an inference algorithm is how good it is at inferring. Some algorithms are better than others. \cite{typeinference}

@@

First, we introduce a new constructor, \verb|Infer : Expr -> Expr|. This will be used to store metavariables which we want to infer. This is a hack we use, ideally we would like to query statix to see if a metavariable is initialized, but as discussed in section \ref{strength-inference} this is not possible.

@@
